\documentclass[11pt]{article}
\usepackage{fullpage}
\usepackage{times}
\usepackage{url}

\newcommand {\doublespace} {\addtolength{\baselineskip}{.5\baselineskip}}
\newcommand {\singlespace} {\addtolength{\baselineskip}{-.333\baselineskip}}

\begin{document}
%\pagestyle{empty}
\renewcommand{\thepage}{DMP-\arabic{page}}
\setcounter{page}{1}

\def\myskip{3ex}

\centerline{\normalsize Rochester Institute of Technology}
\vspace{4 mm}
\centerline{\Large\bf PLASMA: Practical LAbs in Security for Mobile Applications}


\section*{Data Management Plan}

%This plan articulates how sharing of the primary data generated during
%the course of the project for this proposal will be implemented.

\subsection*{Expected Data}

The expected data to be generated during the course of this project are:

% Matt had 7
% Check all these. Feel free to remove 1 or 2
\begin{enumerate}
   \setlength{\itemsep}{.8pt}
    \setlength{\parskip}{0pt}
    \setlength{\parsep}{0pt}


  \item Created modules and supporting materials
  \item Technical papers describing our findings
%  \item Data from participant studies
  \item Course observations and student feedback
%  \item Usage statistics
  \item User feedback generated from course and outreach usage
  \item Course materials, such as lectures and slides, homework assignments, and projects
  \item Student participation and retention rates
  \item Aggregate scores from provided quizzes
  \item Adoption information from non-partner institutions

\end{enumerate}

\subsection*{Data Retention and Storage}
To protect student privacy, we only will share the student learning data in summary form so that we can monitor the level of dissemination for any required reporting. We will also protect the feedback from instructors and use the anonymous responses only for continuous improvement efforts. We will share the results of the surveys and the assessment instruments we develop. Relevant survey instruments will be made available through our website.

Confidential data, including individual survey responses and grade data, will not be released to outside parties. This data will be retained throughout the life of the project in anonymous form and used to generate annual reports and the final report to NSF. Once the project has concluded, this data will be retained for one year, then purged. All non-confidential data generated by this project will be retained for a minimum of three years after the conclusion of the award, including data that is not specifically disseminated as described in the following section. We will use file storage services provided by RIT to ensure secure preservation of data during the retention period.


\subsection*{Data Dissemination}

Technical papers generated during the course of the project will be published in academic journals and conference proceedings. Papers published in venues without archival proceedings, as well as technical reports not otherwise published, will be disseminated via arXiv.

%Related papers and/or conference presentations submitted by the PIs will be made publicly available if allowed by the accepting institution or organization. If the institution or organization accepting the paper or presentation assumes the copyright, we will post a full citation so interested parties can locate the published document.

Data produced from the proposed research activities will be made available either publicly on PI Krutz's website or, for sensitive data, available upon request by other researchers. All created project materials will be made available through the project's website.

Standard reports for the NSF will be generated and electronically submitted through normal channels. We may use summary reports for pedagogical purposes so that other approved institutions may see our results and lessons learned. Annual and final reports will evaluate our adherence to this Data Management Plan. %Shared data will be stored in standard formats, such as text files and XML, whenever it is possible to do so. If binary formats are necessary (e.g., for saving space), utilities for converting this data into human-readable formats will be made available.




%
%The phishing page detection browser plug-in will be released under an
%Open Source License (as defined by the Open Source Initiative) and will
%be published in an open source project repository, such as SourceForge,
%GitHub, or Google code project hosting.
%
%Data produced from the proposed research activities will be made
%available either publicly on PI Wright's website or, for sensitive data,
%available upon request by other researchers. Exceptions to this are the
%RIT phishing training data, which cannot be shared due to RIT policies
%on students and employees, and security incident reports and logs, which
%are sensitive for RIT's security posture. For these data sets, we will
%work with RIT's Global Risk Management team to find ways for other
%researchers to access the data, perhaps in conjunction with the PIs.
%

%
%Curricular materials such as lecture notes and slides will be made
%available via PI Wright's website.
\end{document}
